Pillar 1 - Sequential Pattern Mining

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
finish adding grades. updated RDATA files

@@

```
We save and remove objects:
```{r saving and rm}
#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_not_taken, 
     AR_expanded_taken, AR_expanded_PF, AR_expanded_HL,
     file = "App/AR.RDATA")

# Remove objects
rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL, transactions_Grade,
   course_id_fail, course_id_low,
   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_expanded_taken, AR_expanded_PF, AR_expanded_HL)
```

@@

@@

```
We save and remove objects:
```{r saving and rm SR}
#Saving sequence rules
save(
    SR_taken, SR_PF, SR_HL,

    SR_expanded_taken, SR_expanded_PF, SR_expanded_HL,

@@

#clean unnecessary objects
rm(clean_SR, my_SR, 
   sequences, sequences_PF, sequences_HL, sequences_Grade,
   sequences_expanded, sequences_expanded_PF, sequences_expanded_HL, sequences_expanded_Grade,
   n_students,
   SR_taken, SR_PF, SR_HL,
   SR_expanded_taken, SR_expanded_PF, SR_expanded_HL)

>>>>

AR_Grade <- my_apriori(transactions_Grade)

@@

AR_expanded_Grade <- my_apriori(transactions_expanded_Grade)

```
We save and remove objects:
```{r saving and rm}
#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
     AR_expanded_taken, AR_expanded_PF, AR_expanded_HL, AR_expanded_Grade,
     file = "App/AR.RDATA")

# Remove objects
rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL, transactions_Grade,
   course_id_fail, course_id_low,
   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
   AR_expanded_taken, AR_expanded_PF, AR_expanded_HL, AR_expanded_Grade)
```

@@

SR_Grade   <- my_SR(data = sequences_Grade )

@@

SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade )

```
We save and remove objects:
```{r saving and rm SR}
#Saving sequence rules
save(
    SR_taken, SR_PF, SR_HL, SR_Grade,

    SR_expanded_taken, SR_expanded_PF, SR_expanded_HL, SR_expanded_Grade,

@@

#clean unnecessary objects
rm(clean_SR, my_SR, 
   sequences, sequences_PF, sequences_HL, sequences_Grade,
   sequences_expanded, sequences_expanded_PF, sequences_expanded_HL, sequences_expanded_Grade,
   n_students,
   SR_taken, SR_PF, SR_HL, SR_Grade,
   SR_expanded_taken, SR_expanded_PF, SR_expanded_HL, SR_expanded_Grade)
